MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-05-22 manuscript/manuscript.qmd
submission review revisions
address second round of editorial formatting comments

@@

## Key Resources Table

```{r}
#| results: asis
#| tbl-cap: "Table: Key reagents and resources."

@@

# Author contributions

W.M.O. conceived and designed the analysis. C.A.C., B.A.O., D.R.Z., S.M., K.L., and W.M.O. collected the data. J.D.Y. and W.M.O. contributed data or analysis tools. W.M.O. performed the analysis. W.M.O. drafted the manuscript. All authors participated in interpreting the results and revising the manuscript. All authors approve the final submission.

@@

>>>>

```{r}
#| results: asis
#| tbl-cap: "Key Resources Table"

@@

@@

@@

**Figure 9 - source data 1** Source data for Figure 9C.

**Figure 9 - figure supplement 1 - source data 1** Source data for Figure 9 - figure supplement 1D.

**Figure 9 - figure supplement 1 - source data 2** Source data for Figure 9 - figure supplement 1E.

**Figure 10 - source data 1** Source data for Figure 10C.

**Figure 10 - figure supplement 1 - source data 1** Source data for Figure 10 - figure supplement 1E.

**Figure 10 - figure supplement 1 - source data 2** Source data for Figure 10 - figure supplement 1F.
